Turbulence in compact to giant HII regions

### 2022-01-26 Corr.tex
Javier changes 2022-01-25

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
      log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}
